\documentclass[11 pt]{article} 
\usepackage[left=2cm, top=2cm, right=2cm, bottom=2.5cm, footskip=.5cm]{geometry}
\usepackage{url}
\usepackage{enumitem}

\author{Natalia Zuniga-Garcia}
\title{Peer Review 1}
\date{February 16, 2018}

\begin{document}

\maketitle

\section{Description}

I went trough the documentation available in the student's GitHub page by February 16, 2018.

\begin{itemize}
	\item Student evaluated:  Mauricio Garcia Tec (\url{https://github.com/mauriciogtec/StatsModellingII})
	\item Assignment reviewed: Section 1 (\url{https://mauriciogtec.github.io/StatsModellingII/index.html})

\end{itemize}
	


\section{General Comments}
\begin{itemize}
	\item I really like the way you present your results by using a html document. I make it easier to go through the documentation from your GitHub page. Also, it looks more professional.
	\item You presented the solution of the exercises providing a wide description of the procedure, which makes easier to understand the process you followed.
	\item Your solutions are very straightforward and easy to follow.
	\item You provided extended comments from the final solution of some exercises that allowed me to better understand the concept we were evaluating.

	
\end{itemize}

\section{Specific Comments}
\begin{itemize}
		\item \textbf{Exercise 2.14:} I appreciate the approach you provided for generating multivariate normal variables, which you also explained it on the board during class. I consider that the way you explained it made me  understand the concept better.
		\item \textbf{Exercise 2.15:} In this exercise I used other procedure that was more difficult.  I think the way you solved it is clearer than mine.

\end{itemize}

\section{Summary}
Dear Mauricio, 

I tried to provide you good feedback. I tried check in detail your documentation so you can improve. In the process I learned a lot, I learned from your solution and by reviewing it. For instance, I found that you used a simpler way to probe some of the exercises. I hope this help you in your next assignments, it did help me! 

\end{document}